### 2018-10-03 paper/paper.tex
Usage of observation.

% \MS{name clash: LEAD TIME Syndrome with no LEAD TIME?}
Despite this theoretical observation the name lead time syndrome may be under question. However, as
in cases as given in the proof above the lead time follows the order release decisions and in
practice order releases are usually determined by the lead time (or flow time) the wording can be
considered as appropriate.

@@

Consider a single product one-stage flow-shop manufacturing system that releases orders from the
order pool into the production system by an external mechanism.
%
Usually the orders are released based on the observed (average) flow time of the last finished
orders. However, our method does not presuppose such an interdependence for detecting the lead time
syndrome as it works directly on (parts of) the \WIP{}-level of the system.
%
% Intuitively the method works as
% follows. By measuring the change of the average \WIP{}-level over time and comparing this to the
% average releases into the system it can infer the desired property.
%
We denote the demand rate at time $t \geqslant 0$ as $\dr{t}$, and the demand for the item during
the period defined by timestamps $t_{2} \geqslant t_{1} \geqslant 0$ as $\di{t_{1}}{t_{2}}$.
Similarly we denote the order release rate as $\rr{t}$ and the releases within a period as
$\ri{t_{1}}{t_{2}}$. Each work-station $i$ is equipped with a queue $\q_{i}$ on which released
orders are appended according to a given routing and from there handed over to the work-station if
only if the work-station is empty and the order is at the head of the queue. Thus we allow parallel
processing of unique orders with non-shared queues in the setup. In case of shared queues in this
single item setup the work-station shall be considered as a single work-station. The size of a queue
$\size{\q_{i}} \geqslant 0$ is given by the number of orders within the queue.

>>>>

% \MS{name clash: LEAD TIME Syndrome with no LEAD TIME?}
Despite this theoretical observation the name lead time syndrome may be under question. However, as
in cases like the one given in the proof above the lead time follows the order release decisions and
in practice order releases are usually determined by the lead time (or flow time), the wording can
be considered as appropriate.
%
Nonetheless, our method is based on this observation. First we do not consider the lead time as
input variable to the method, then we do not suppose an interconnection between the \WIP{}-level
with the release decision procedure, and finally we do not restrict our method on any particular
order release pattern.

@@

Consider a single product one-stage flow-shop manufacturing system that releases orders from the
order pool into the production system by an external mechanism.
%
Usually the orders are released based on the observed (average) flow time of the last finished
orders. However, our method does not presuppose such an interdependence for detecting the lead time
syndrome as it works directly on (parts of) the \WIP{}-level of the system. Thus our approach is
also able to observe systematic releasing misbehavior, referred to as \LTS{}, which do not consider
the lead time as depended variable for the release decisions.
%
% Intuitively the method works as
% follows. By measuring the change of the average \WIP{}-level over time and comparing this to the
% average releases into the system it can infer the desired property.
%
We denote the demand rate at time $t \geqslant 0$ as $\dr{t}$, and the demand for the item during
the period defined by timestamps $t_{2} \geqslant t_{1} \geqslant 0$ as $\di{t_{1}}{t_{2}}$.
Similarly we denote the order release rate as $\rr{t}$ and the releases within a period as
$\ri{t_{1}}{t_{2}}$. Each work-station $i$ is equipped with a queue $\q_{i}$ on which released
orders are appended according to a given routing and from there handed over to the work-station if
only if the work-station is empty and the order is at the head of the queue. Thus we allow parallel
processing of unique orders with non-shared queues in the setup. In case of shared queues in this
single item setup the work-station shall be considered as a single work-station. The size of a queue
$\size{\q_{i}} \geqslant 0$ is given by the number of orders within the queue.
